---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pgfsr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![R-CMD-check](https://github.com/poissonconsulting/pgfsr/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/pgfsr/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/pgfsr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/pgfsr?branch=main)
<!-- badges: end -->

`pgfsr` is an R client for [pg_featureserv](https://github.com/CrunchyData/pg_featureserv), a RESTful web service that provides access to spatial data stored in PostGIS tables, as well as spatial processing capability based on PostGIS spatial functions.  

For more information on pg_featureserv:  
- [User Guide](https://access.crunchydata.com/documentation/pg_featureserv/1.2.0/)   
- [API Summary](https://github.com/CrunchyData/pg_featureserv/blob/master/API.md#feature-collections)  
- [Github Page](https://github.com/CrunchyData/pg_featureserv)  

### Work with collections

Get information about collections or a single collection:  

* [`pgf_collections()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collections.html)  
* [`pgf_collection_properties()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_properties.html)  
* [`pgf_collection_description()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_description.html)  
* [`pgf_collection_crs()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_crs.html)  
* [`pgf_collection_bbox()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_bbox.html)  
* [`pgf_collection_geometry_type()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_geometry_type.html)  

Query features or a single feature from a collection:  

* [`pgf_collection_features()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_features.html)  
* [`pgf_collection_feature()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_collection_feature.html)  

### Work with functions

Get information about functions or a single function:  

* [`pgf_functions()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_functions.html)  
* [`pgf_function_properties()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_function_properties.html)  
* [`pgf_function_parameters()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_function_parameters.html)  
* [`pgf_function_description()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_function_description.html)

Execute a spatial function and get result:  

* [`pgf_function_result()`](https://poissonconsulting.github.io/pgfsr/reference/pgf_function_result.html)

## Installation

You can install the development version of pgfsr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("poissonconsulting/pgfsr")
```

## Demonstration
Lookup available collections in BC Freshwater Atlas:
```{r}
base_url <- "https://features.hillcrestgeo.ca/"
path <- "fwa"
collections <- pgfsr::pgf_collections(base_url = base_url, path = path)
collections$id
```

Get Sangan River from the stream network collection:
```{r}
coll <- "whse_basemapping.fwa_stream_networks_sp"
river <- pgfsr::pgf_collection_features(coll, base_url = base_url, path = path,
                 filter = list(gnis_name = "Sangan River"))
class(river)
river[1:5, 1:4]
```

## Code of Conduct

Please note that the pgfsr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
